\documentclass[letterpaper]{config}

\begin{document}
\Header
    {Priyansh Jain} % name
    {Indore, India}
    {+91 9770423319} % phone number
    {me.priyanshjain@gmail.com} % email
    {priyansh-pj} % https://linkedin.com/in/_______
    {priyansh-pj}
    % {As a dedicated tech enthusiast and aspiring data scientist, I possess a fervent drive to excel in my work and a remarkable aptitude for acquiring new skills swiftly. Proficient in multiple programming languages, I bring extensive experience collaborating effectively within teams. I embody a diligent work ethic and exhibit meticulousness in every task. My unwavering commitment to delivering excellence enables me to consistently achieve outstanding results. I am eager to demonstrate my value as a valuable asset to your esteemed team.}

\section{Work Experience}
\WorkExperience
    {Python Development Lead} % job title
    {IES - IPS Academy} % company name
    {Mar 2022 -- Present} % beginning and end of employment. If currently employed write " - Present"
    {Indore, India} % city, country of employment
    {
        \item Developed and optimized 10+ Python scripts and applications, streamlining critical processes such as grade calculation, NBA analysis, and backend development. and leading project for 30\% efficiency increase.
        \item Overhauled service processes, enhancing communication flow across 10 departments. Achieved an impressive 75\% reduction in paperwork and a notable 40\% efficiency boost.
        \item Contributed to the development and testing of APIs for a latest CMS portal, ensuring seamless integration and delivering a significant 30\% performance boost.
        \item Implemented and maintained a college management website using CodeIgniter and SQL, elevating functionality and performance.
        \item Resolved technical issues, implemented crucial enhancements, and achieved outstanding results, including a 20\% surge in website performance and a remarkable 40\% reduction in page loading time.
        \item Streamlined the website's efficiency and functionality, optimizing data management and organization for over 1500+ students across 10+ different engineering courses, aligning with the institution's rigorous standards.
        \item Conducted thorough code reviews and provided technical guidance to a team of 5+ junior developers, elevating code quality and improving software efficiency.
    } 
    
\section{Project}
\Project
    {DataBliss} % project name
    {Django, React, PostgreSQL} % technologies
    {https://github.com/priyansh-pj/DataBliss}% https://github.com/____/____
    {
        \item DataBliss is an ERP web application aiming to optimize organizational efficiency by 30\% using Django, React, and PostgreSQL.
        \item Prioritized the development of a user-friendly and intuitive interface, resulting in a seamless user experience and broad adoption within the organization.
        \item Ensured seamless access and usability across various devices and operating systems through cross-platform compatibility.
        \item Implemented comprehensive testing protocols for DataBliss, resulting in improved reliability, security, and effectiveness; reduced troubleshooting time by 30\% and increased user satisfaction by 25\%.
        \item Recognized as the runner-up in the Udaan competition for the successful implementation and significant impact of DataBliss in enhancing organizational efficiency by 30\%.
    }


\section{Accomplishments}


\Responsibility
    {Vice Captain - CSE-Chess Team (IPS Academy)} % school name
    {2 times Winner of College (Swaranjali) Chess Tournament and Runner-up in District Nodal’s Competition} % credential name
    {Jan 2021- Present} % date of graduation

\Responsibility
    {Member - Scintilla Literary Club} % school name
    {IPS Academy} % credential name
    {Apr 2021- Mar 2022} % date of graduation

\Responsibility
    {Volunteered - Ek Bharat Shreshtha Bharat} % school name
    {IPS Academy} % credential name
    {Jun 2022} % date of graduation
    
\Responsibility
    {Co-Lead - Google Student Developer Club} % school name
    {IPS Academy} % credential name
    {May 2022- Apr 2023} % date of graduation

    
    
\section{Education}

\EducationExperience
    {IES - IPS Academy, Indore} % school name
    {Bachelor of Technology in Data Science} % credential name
    {Jul 2020- Jul 2024} % date of graduation
    {CGPA – 8}
    {
        \item Actively engaged in a wide range of co-curricular activities, highlighting a strong dedication to holistic development beyond academics.
        \item Exhibited strategic thinking, teamwork, and discipline as a valuable member of the Chess Team, achieving notable success in multiple tournaments.
        \item Demonstrated enthusiasm, technical expertise, and strong collaboration skills by actively participating in hackathons and coding competitions.
    } 

% \EducationExperience
%     {Sarafa Vidhya Niketan, Indore} % school name
%     {High School, 12th Class} % credential name
%     {2020} % date of graduation
%     {P.C.M. + C.S}
%     {
%         \item Proactively engaged in 2+ inter-school Hackathons, effectively demonstrating exceptional problem-solving skills and a collaborative spirit.
%         \item Showcased technical prowess in Tech-exhibitions, delivering compelling presentations on innovative projects, garnering recognition and commendations.
%         \item Evidenced a solid foundation in science and computer science subjects, reflecting a comprehensive understanding and proficiency in these domains.
%     }


    
\section{Technical Skills}

\SkillList{
    \SkillItem{Languages}{: Python, Javascript, PHP, HTML, CSS, C, C++}
    \SkillItem{Frameworks}{: Django, CodeIgniter}
    \SkillItem{Libraries}{: Numpy, Pandas, Scikit-Learn, React.js, Bootstrap, Ajax, jquery}
    \SkillItem{Tools}{: Git, Postman, Unix, Jupyter Notebook, Excel, PowerBI, Tableau}
    \SkillItem{Databases}{: PostgreSQL, MongoDB}
    \SkillItem{Skills}{: Statistics and Probability, Data Visualization, Web Development}
    
}

\end{document}
